On-the-fly Algorithms for GKAT Equivalences \thanks{Identify applicable funding agency here. If none, delete this.}

### 2025-01-19 main.tex
fix typo
small fix

Because of the functoriality, we can show that two states are infinite-trace equivalent implies these two states are finite-trance equivalent.
This gives us more tool in proving semantic equivalence between two states in GKAT coalgebras: proving bisimulation of these two states in the \emph{non-normalized} GKAT coalgebra can also obtain semantic equivalence for two states.

@@

The final optimization that we perform is collapsing the sets of boolean expressions of \(\hat{\epsilon}(s)\) into a single boolean expression. Basically, each \(\hat{\epsilon}(s)\) is represented by the boolean disjunction of its elements. Consider the guard operation defined in \Cref{sec:symb-gkat-construction}.
\begin{align*}
    ⟨\hat{\epsilon_1}(s_1)|\hat{\epsilon_2}(s_2) & ≜ \{b ∧ c ∣ b ∈ \hat{\epsilon_1}(s_1), c ∈ \hat{\epsilon_2}(s_2)\}
\end{align*}
If \(\hat{\epsilon_1}(s_1)\) and \(\hat{\epsilon_2}(s_2)\) are sets of boolean expressions, then the guard operation would produce a set whose size is proportional to \(|\hat{\epsilon_1}(s_1)| \times |\hat{\epsilon_2}(s_2)|\). However, if the collapsed representation is used, \(\hat{\epsilon_1}(s_1)\) and \(\hat{\epsilon_2}(s_2)\) become just boolean expressions instead of sets of expressions. The guard operation now produces a single boolean expression. The distributivity of boolean conjunction and disjunction ensures the correctness of this optimization.

>>>>

Because of the functoriality, we can show that two states are infinite-trace equivalent implies these two states are finite-trace equivalent.
This gives us more tool in proving semantic equivalence between two states in GKAT coalgebras: proving bisimulation of these two states in the \emph{non-normalized} GKAT coalgebra can also obtain semantic equivalence for two states.

@@

The final optimization that we perform is collapsing the boolean expression set \(\hat{\epsilon}(s)\) into a single boolean expression. Basically, each \(\hat{\epsilon}(s)\) is represented by the boolean disjunction of its elements. Consider the guard operation defined in \Cref{sec:symb-gkat-construction}.
\begin{align*}
    ⟨\hat{\epsilon_1}(s_1)|\hat{\epsilon_2}(s_2) & ≜ \{b ∧ c ∣ b ∈ \hat{\epsilon_1}(s_1), c ∈ \hat{\epsilon_2}(s_2)\}
\end{align*}
If \(\hat{\epsilon_1}(s_1)\) and \(\hat{\epsilon_2}(s_2)\) are sets of boolean expressions, then the guard operation would produce a set whose size is proportional to \(|\hat{\epsilon_1}(s_1)| \times |\hat{\epsilon_2}(s_2)|\). However, if the collapsed representation is used, \(\hat{\epsilon_1}(s_1)\) and \(\hat{\epsilon_2}(s_2)\) become just boolean expressions instead of sets of expressions. The guard operation now produces a single boolean expression. The distributivity of boolean conjunction and disjunction ensures the correctness of this optimization.
